\section{2}
\subsection{}
The j loop goes through j=1 to j=3. At each itteration of the for loop
we call the function inside of myFuns of j, or myFuns[[j]]. The trick here,
why each myFuns returns 3, is that the function inside of each myFuns part
returns i, and seeing as i is not redefined inside of the current for loop,
R goes looking into the global environment. Here it finds i, and the last value
that i had, and still has, is 3. As such, each call of myFuns calls a function 
which returns i and as such, returns 3.
\subsection{}
The second i loop displays the behavior we "expect". Each itteration of the loop calls the function inside of the ith index of myFuns. This function, the same
in each index, is asked to return the value of i, so, it goes looking for i. Not
finding i in itself, it goes up one environment and finds i in the loop that called it.
Here, it finds the value of i which the loop is using, which progresses through
1:3. 
\subsection{}
For the j loop the answer is obvious. The function in myFuns of j is called
and it is asked to return i. Considering that it has no value of i in its own self, it goes and looks in its parent environment of funGenerator in which the value of i is the last value of the for loop and is thus, 3. This behavior explains the behavior seen in the global i loop, before R goes and looks in global for a value of i, the function in myFuns of i is asked to look for i in the envionrment of FunGenerator and as such, finds i=3. 

\section{3}
So, the first "frame" is the global frame and it's environment is the global
environment. In case of a clean R session and just inputting the given code,
this "frame" is populated by no objects and ls returns a [0]. The global "frame
" has frame number 0. The next function, or really the first, that is called
is the sapply function with frame number 1. The objects that exist are "FUN", 
"simplify", "USE.NAMES", and "X". The next function that gets called is the
"ls" function with frame number 2 and is populated with objects "FUN" and "X".
The last function that is called is sys.frame with frame number 3 and is only
populated by object "X".


